Incremental tactics

### 2012-05-09 doc/papers/LFMTP2012/paper.tex
paper

\begin{align*}
  K &\gequal
  \prd x A K \gor
  \type &
  \text{Kind}\\
  A &\gequal
  \prd x A A \gor
  \app {\cst a} S &
  \text{Type family} \\
  M &\gequal
  \lam x M \gor
  F &
  \text{Object} \\
  F &\gequal \app H S
  \gor
  \smeta X \sigma &
  \text{Application} \\
  H &\gequal
  \var x \gor
  \cst c &
  \text{Head}\\
  S &\gequal
  \spinenil \gor
  \spinecons M S &
  \text{Spine}\\
  \sigma &\gequal
  \msubstnil \gor
  \msubstcons \sigma x M &
  \text{Parallel substitution} \\
  \Gamma &\gequal
  \envnil \gor
  \envcons \Gamma x A &
  \text{Environment}
\end{align*}

@@

% TODO com M check/F infer

@@

@@

% TODO parler de la redondance en LF normal

@@

  \fbox{$\jm\mr\Gamma M A \mmr {M'}$}
  \qquad
  Object

@@

  \fbox{$\jf\mr\Gamma F \mmr F A$}
  \qquad
  {Application}

@@

    % Sliceable
    \infer{
      \jh\mr\Gamma H A \annsliceable
      \and
      \jl\mr\Gamma A S \mmr {S'} {A'}
      \and
      \stren{\Gamma, \app H {S'}}=\Gamma'
      \and
      \text{$\meta X$ fresh in $\mr$}
    }{
      \jf\mr\Gamma {\app H S} {\mapadd\mmr{\meta X}{(\Gamma'\vdash
          {\app H {S'}}:A)}} {\smeta X{\msubstid{\Gamma'}}} {A'}
    }

@@

The main judgement is application typing $\jf\mr\Gamma F \mmr {F'} A$,
which means that in repository $\mr$ and environment $\Gamma$, the
applicative term $F$ is well-typed of type $A$, and the slicing of $F$
produces a new repository $\mmr$. The object $F'$ is the
\emph{residual} of this operation: only certain kind of applications
are sliced, and it is possible that the ``tip'' of application $F$ is
not sliced (because it is declared as non-sliceable). In that case,
$M$ is this tip; if $F$ is directly sliceable, then $M$ is the
metavariable referring to it.

>>>>

\begin{align*}
  K &\gequal
  \prd x A K \gor
  \type &
  \text{Kind}\\
  A &\gequal
  \prd x A A \gor
  \app {\cst a} S &
  \text{Type family} \\
  M &\gequal
  \lam x M \gor
  F &
  \text{Canonical object} \\
  F &\gequal \app H S
  \gor
  \smeta X \sigma &
  \text{Atomic object} \\
  H &\gequal
  \var x \gor
  \cst c &
  \text{Head}\\
  S &\gequal
  \spinenil \gor
  \spinecons M S &
  \text{Spine}\\
  \sigma &\gequal
  \msubstnil \gor
  \msubstcons \sigma x M &
  \text{Parallel substitution} \\
  \Gamma &\gequal
  \envnil \gor
  \envcons \Gamma x A &
  \text{Environment}
\end{align*}

@@

@@

We distinguish syntactically between \emph{checkable} and
\emph{inferrable} objects (resp. \emph{canonical} and \emph{atomic}),
an idea dating back to \cite{pierce2000local}: canonical objects are
checked against a given type, whereas we can synthesize the type of
atomic objects; the coercion from the first to the second will be the
place where to verify equality between the synthesized type and the
given one.

@@

% TODO parler d'effacer les R et retomber sur LF
% TODO expl. c'est tout comme LF sauf qqes règles...
% TODO parler de la redondance en LF normal

@@

  \fbox{$\jm\mr\Gamma M A \mmr {M'}$}
  \qquad
  Canonical object

@@

  \fbox{$\jf\mr\Gamma F \mmr F A$}
  \qquad
  {Atomic object}

@@

    % Sliceable
    \infer{
      \jh\mr\Gamma H A \annsliceable
      \and
      \jl\mr\Gamma A S \mmr {S'} {A'}
      \and
      \stren{\Gamma, \app H {S'}}=\Gamma'
    }{
      \jf\mr\Gamma {\app H S} {\mapadd\mmr{\meta X}{(\Gamma'\vdash
          {\app H {S'}}:A)}} {\smeta X{\msubstid{\Gamma'}}} {A'}
    }
    \quad\text{($\meta X$ fresh in $\mr$)}

@@

The main judgement is atomic object typing $\jf\mr\Gamma F \mmr {F'}
A$, which means that in repository $\mr$ and environment $\Gamma$, the
applicative term $F$ is well-typed of type $A$, and the slicing of $F$
produces a new repository $\mmr$. The object $F'$ is the
\emph{residual} of this operation: only certain kind of applications
are sliced, and it is possible that the ``tip'' of application $F$ is
not sliced (because it is declared as non-sliceable). In that case,
$M$ is this tip; if $F$ is directly sliceable, then $M$ is the
metavariable referring to it.
